Statistical mechanics of Wigner negativity and magic states in quantum computation

### 2021-06-07 notes/notes.tex
Changes made, some rearrangement required

>>>>

\begin{figure}[t]
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:Strange}%
    \includegraphics[height=2cm]{figs/Strangestate.pdf}
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $|0\>\<0|$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:Strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
    }%
    \label{fig:wstate_examples}
\end{figure}
